Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2023-03-11 analysis/hypotheses.qmd
Remove questions and methods section

- **H~1a~**: If states formally derogate from international treaty provisions, then they are less likely to use discriminatory policy measures during the pandemic.
- **H~1b~**: If states formally derogate from international treaty provisions, then they are less likely to violate non-derogable rights
- **H~1c~**: If states formally derogate from international treaty provisions, then they are less likely to impose measures with no time limits.

@@

- **H~2a~**: If states are repressive towards civil society organizations, then they are more likely to violate non-derogable rights.
- **H~2b~**: If states are repressive towards civil society organizations, then they are more likely to use discriminatory policy measures during the pandemic.
- **H~2c~**: If states are repressive towards civil society organizations, then they are more likely to engage in abusive enforcement of measures instated to deal with the pandemic.
- **H~2d~**: If states are repressive towards civil society organizations, then they are more likely to impose limits on media freedom.

>>>>

- **H~1a~**: If states formally derogate from international treaty provisions, then they are less likely to use discriminatory policy measures during the pandemic.
- **H~1b~**: If states formally derogate from international treaty provisions, then they are less likely to violate non-derogable rights.
- **H~1c~**: If states formally derogate from international treaty provisions, then they are less likely to impose measures with no time limits.

@@

- **H~2a~**: If states are repressive towards civil society organizations, then they are more likely to violate non-derogable rights.
- **H~2b~**: If states are repressive towards civil society organizations, then they are more likely to use discriminatory policy measures during the pandemic.
- **H~2c~**: If states are repressive towards civil society organizations, then they are more likely to engage in abusive enforcement of measures instated to deal with the pandemic.
- **H~2d~**: If states are repressive towards civil society organizations, then they are more likely to impose limits on media freedom during the pandemic.

### 2023-03-11 index.qmd
Remove questions and methods section

---
title: "Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19"
format:
  html:
    code-tools: false
sidebar: false
---

- Suparna Chaudhry (Lewis & Clark College)
- Audrey L. Comstock (Arizona State University)
- Andrew Heiss (Georgia State University)

>>>>

---
title: "Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19"
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  orcid: 0000-0003-3506-7590
  url: https://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Audrey L. Comstock
  affiliation: Arizona State University
  orcid: 0000-0003-1772-5350
  url: https://audreylcomstock.weebly.com/
  email: audrey.comstock@asu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  orcid: 0000-0002-3948-3914
  url: https://www.andrewheiss.com
  email: aheiss@gsu.edu
format:
  html:
    code-tools: false
sidebar: false
---
